Untitled

### 2020-09-07 manuscript/manuscript.Rmd
address xavier's requests

```{r}
set.seed(4286)
train <- sample(unique(data$id), size = .7*length(unique(data$id)), replace = FALSE)
df_train <- dat[data$id %in% train, ]
df_test <- dat[!data$id %in% train, ]
```

@@

```{r}
# Run model with many trees to check convergence
check_conv <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 20000)
# Plot convergence trajectory
```

@@

@@

# X should contain only retained moderators, clustering variable, and vi
X <- df_train[, c("vi", mods)]

>>>>

```{r}
set.seed(4286)
train <- sample(unique(data$id), size = .7*length(unique(data$id)), replace = FALSE)
yaml::write_yaml(train, "split.yml")
train <- yaml::read_yaml("split.yml")
df_train <- dat[data$id %in% train, ]
df_test <- dat[!data$id %in% train, ]
```

@@

```{r}
# Run model with many trees to check convergence
set.seed(6473)
check_conv <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 20000)
# Plot convergence trajectory
```

@@

```{r, echo = FALSE}
# Run recursive preselection, store results in object 'preselect'
set.seed(73829)
mf_rep <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 10000)
preselected <- preselect(mf_rep,
                         replications = 100
                         )
# Plot the results
plot(preselected)
# Retain only moderators with positive variable importance in more than
# 50% of replications
retain_mods <- preselect_vars(preselected, cutoff = .95)

@@

# X should contain only retained moderators, clustering variable, and vi
X <- df_train[, c("vi", retain_mods)]
